A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-11 manuscript.Rmd
explain when exactly we plan to use real data

If you have written a [Preregistration as Code] you can swap the data file and reproduce the project.
In fact, before the`r link("https://github.com/aaronpeikert/repro-tutorial/releases/tag/ v0.0.1-preregistration", "preregistration")` were the results below on simulated data, only after we preregistered the whole manuscript, they were based on actual data from https://openpsychometrics.org/_rawdata/.

@@

Note that both this tutorial as well as our article on the reproducible workflow [@Peikert2019] were created using this workflow and can be reproduced from their source code repositories.
<!-- maybe we add here the real data? #25 -->

>>>>

If you have written a [Preregistration as Code] you can swap the data file and reproduce the project.
In fact, till after we preregistered the study `r link("https://github.com/aaronpeikert/repro-tutorial/releases/tag/ v0.0.1-preregistration", "preregistration")` were the results below based on simulated data.
Only after we preregistered the whole manuscript and upon submission, they were based on actual data from https://openpsychometrics.org/_rawdata/.

@@

Note that both this tutorial as well as our article on the reproducible workflow [@Peikert2019] were created using this workflow and can be reproduced from their source code repositories.
